\documentclass[11pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{array}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\titleformat{\section}
{\large\bfseries}
{SECTION \thesection:}
{0.5em}
{}

\begin{document}

\begin{center}
{\LARGE \textbf{SAFETY DATA SHEET (SDS)}}\\[6pt]
{\Large \textbf{ALREHAB Royal Eau de Parfum Spray}}\\
{\large \textbf{50ml (1.7 oz) Men Perfume}}\\[6pt]
Prepared according to OSHA Hazard Communication Standard\\
29 CFR 1910.1200
\end{center}

\vspace{10pt}

\section{IDENTIFICATION}

\textbf{Product Identifier:} ALREHAB Royal Eau de Parfum Spray

\textbf{Product Type:} Cosmetic Fragrance / Eau De Parfum

\textbf{Brand:} Al Rehab

\textbf{Manufacturer:} Al Rehab Perfumes LLC

\textbf{Country of Origin:} United Arab Emirates

\textbf{Recommended Use:} Personal fragrance / cosmetic use

\textbf{Emergency Contact:} CHEMTREC USA +1-800-424-9300

\section{HAZARDS IDENTIFICATION}

\textbf{Classification:}
\begin{itemize}[noitemsep]
    \item Flammable Liquid -- Category 3
    \item Skin Irritation -- Category 2
    \item Skin Sensitization -- Category 1
\end{itemize}

\textbf{Signal Word:} Danger

\textbf{Hazard Statements:}
\begin{itemize}[noitemsep]
    \item H226: Highly flammable liquid and vapor
    \item H315: Causes skin irritation
    \item H317: May cause allergic skin reaction
\end{itemize}

\textbf{Precautionary Statements:}
\begin{itemize}[noitemsep]
    \item Keep away from heat, sparks, open flames, and hot surfaces.
    \item Avoid contact with eyes and skin.
    \item Use only in a well-ventilated area.
    \item Keep container tightly closed.
\end{itemize}

\section{COMPOSITION / INFORMATION ON INGREDIENTS}

\begin{longtable}{|p{2.3in}|p{1.5in}|p{1.5in}|}
\hline
\textbf{Ingredient} & \textbf{CAS Number} & \textbf{Concentration} \\
\hline
Ethanol / Alcohol Denat. & 64-17-5 & 70--90\textbackslash\{\}\% \\
Fragrance Compounds & Proprietary & 5--15\textbackslash\{\}\% \\
Water / Aqua & 7732-18-5 & 1--5\textbackslash\{\}\% \\
Fixatives / Stabilizers & Proprietary & <5\textbackslash\{\}\% \\
\hline
\end{longtable}

Exact fragrance composition is proprietary.

\section{FIRST AID MEASURES}

\textbf{Eye Contact:} Rinse cautiously with water for several minutes. Remove contact lenses if present and easy to do. Continue rinsing.

\textbf{Skin Contact:} Wash affected area with soap and water. Discontinue use if irritation occurs.

\textbf{Inhalation:} Move person to fresh air if irritation occurs.

\textbf{Ingestion:} Do not induce vomiting. Seek medical advice if swallowed.

\section{FIRE-FIGHTING MEASURES}

\textbf{Suitable Extinguishing Media:} Carbon dioxide, dry chemical powder, alcohol-resistant foam.

\textbf{Specific Hazards:} Flammable liquid and vapor. Vapors may form explosive mixtures with air.

\textbf{Protective Equipment:} Firefighters should wear appropriate protective equipment and self-contained breathing apparatus if necessary.

\section{ACCIDENTAL RELEASE MEASURES}

Remove ignition sources.

Ventilate the area.

Absorb spill with inert material such as sand, earth, or vermiculite.

Dispose of collected material according to local, state, and federal regulations.

\section{HANDLING AND STORAGE}

\textbf{Handling:}
\begin{itemize}[noitemsep]
    \item Avoid spraying near open flame or ignition sources.
    \item Avoid contact with eyes.
    \item Use only as directed.
\end{itemize}

\textbf{Storage:}
\begin{itemize}[noitemsep]
    \item Store in a cool, dry, well-ventilated place.
    \item Keep away from direct sunlight, heat, sparks, and flames.
    \item Keep container tightly closed.
\end{itemize}

\section{EXPOSURE CONTROLS / PERSONAL PROTECTION}

\textbf{Occupational Exposure Limit:}

Ethanol OSHA PEL: 1000 ppm

\textbf{Personal Protective Equipment:}

No special PPE required for normal consumer cosmetic use.

\textbf{Ventilation:}

Use in a well-ventilated area.

\section{PHYSICAL AND CHEMICAL PROPERTIES}

\begin{longtable}{|p{2.5in}|p{3in}|}
\hline
\textbf{Property} & \textbf{Value} \\
\hline
Appearance & Clear liquid \\
\hline
Odor & Fragrance \\
\hline
Physical State & Liquid spray \\
\hline
Flash Point & Approximately 16--25$^\circ$C \\
\hline
Boiling Point & Approximately 78$^\circ$C \\
\hline
Solubility & Partially soluble in water \\
\hline
Flammability & Flammable liquid and vapor \\
\hline
\end{longtable}

\section{STABILITY AND REACTIVITY}

\textbf{Reactivity:} No dangerous reaction known under normal use.

\textbf{Chemical Stability:} Stable under recommended storage conditions.

\textbf{Conditions to Avoid:} Heat, sparks, open flames, direct sunlight.

\textbf{Incompatible Materials:} Strong oxidizing agents.

\textbf{Hazardous Decomposition Products:} Carbon monoxide and carbon dioxide may form during combustion.

\section{TOXICOLOGICAL INFORMATION}

May cause mild skin or eye irritation.

May cause allergic reaction in sensitive individuals.

Low toxicity expected under normal cosmetic use.

\section{ECOLOGICAL INFORMATION}

No significant environmental hazard expected under normal consumer use.

Avoid release of large quantities into drains, waterways, or soil.

\section{DISPOSAL CONSIDERATIONS}

Dispose of contents and container in accordance with local, state, and federal regulations.

Do not dispose of large quantities into drains.

Recycle packaging where possible.

\section{TRANSPORT INFORMATION}

\begin{longtable}{|p{2.5in}|p{3in}|}
\hline
\textbf{UN Number} & UN1266 \\
\hline
\textbf{Proper Shipping Name} & Perfumery Products \\
\hline
\textbf{Hazard Class} & 3 \\
\hline
\textbf{Packing Group} & II \\
\hline
\textbf{Transport Hazard} & Flammable Liquid \\
\hline
\end{longtable}

\section{REGULATORY INFORMATION}

Prepared according to OSHA Hazard Communication Standard 29 CFR 1910.1200.

Product is intended for cosmetic use.

All components are used in accordance with applicable cosmetic fragrance regulations.

\section{OTHER INFORMATION}

\textbf{NFPA Rating:}

Health: 2

Flammability: 4

Reactivity: 0

\vspace{10pt}

This Safety Data Sheet is provided for safe handling, storage, transportation, and regulatory review of cosmetic fragrance products.

\vfill

\begin{center}
\textbf{End of Safety Data Sheet}
\end{center}

\end{document}
